---
title: "GeoR_Assingment1_KEY_Katchen"
author: "Jordan Katchen"
date: "2023-02-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Key
This document contains solutions to all the questions in Katchen's Geo Computation in R Assignment 1. Because there are many ways to accomplish the questions outlined in the original assignment, your answers may look slightly different than the ones found here. The main goal is to have similar final outputs.

## library
This chunk contains all the packages required to complete this assignment. You may load additional packages if you wish, however, it is not required.

```{r}
library(rgbif)     # Used to load GBIF data
library(sf)
library(tidyr)
library(rnaturalearth)        # Used to load map data
library(geodata)    # Used to load in raster data
library(terra)
```

## Data Load
The bellow chunks load the data required for this assignment.

Search GBIF for Japanese green woodpecker (Picus awokera) occurrence records. Limit the results to 2500. Returns an object of class gbif, which is a S3 class list, with slots for metadata (meta), the occurrence data itself (data), the taxonomic hierarchy data (hier), and media metadata (media).
```{r}
GBIF <- occ_search(
  scientificName = "Picus awokera",
  limit = 2500
)
```

Isolating the occurrence data from the gbif object.
```{r}
Occurence_Data <- GBIF$data
```

Loading in a detailed map of the world from the naturalearth database. The map is loaded in as an sf object.
```{r}
World_map_detail <- ne_download(
  scale = 10,
  type = "countries",
  category = c("cultural"),
  destdir = tempdir(),
  load = TRUE,
  returnclass = c("sf")
)
```

## Assingnment Key

### Part 1 (1 Available Point)
The first step will be to remove all rows with NA values in the latitude and longitude columns from the Occurence_Data. Note, there are many different ways to accomplish this task!

**KEY:** This is just one of many ways to remove NA values.

**Grading:** 1 point for successfully removing NA rows.

```{r}
Occurence_Data <- Occurence_Data %>% drop_na(decimalLatitude) #Remove rows with no lat data
Occurence_Data <- Occurence_Data %>% drop_na(decimalLongitude) #Remove rows with no Long data
```

### Part 2 (2 Available Point)
Convert the Occurence_Data to an sf object.

**KEY:** Don't forget to assign a CRS! Looking at the "geodeticDatum" column in Occurence_Data, you see that all occurrence records use WGS84. This is typical for GBIF data.

**Grading:** 1 point for successfully converting to a sf object. 1 point for assigning the correct CRS.

```{r}
Occurence_Data_sf <- st_as_sf(Occurence_Data, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```

### Part 3 (1 Available Point)
Where in the world are Japanese green woodpeckers found? Plot the occurrence records on a world map.

**KEY:** This figure shows that this species of woodpecker is endemic to Japan and its surrounding islands.

**Grading:** 1 point for successfully creating a map that illustrates where in the world these occurrence records are located.

```{r}
plot(st_geometry(World_map_detail)) #Plot the world map
plot(st_geometry(Occurence_Data_sf), add = TRUE, cex = .01, col = "red") #Add the occurrence records onto to world map. The cex argument determines the symbol size for occurrence points. The col argument determines the colour of the occurrence points.
```

### Part 4 (1 Available Point)
Now that you have narrowed down the region of the world these woodpeckers are found, create a smaller map, just large enough to include all the occurrence records. Try your best to make your map visually appealing and functional, so feel free to be creative.

**Grading:** 1 point for successfully creating a zoomed in map of Japan. 1/2 bonus point available for maps that use colour. 1/2 bonus point available for maps that include the borders of neighboring countries.

```{r}
japan <- World_map_detail[World_map_detail$SOVEREIGNT == "Japan", ] #Creating an sf object that only contains a single row for Japan.
plot(st_geometry(japan), expandBB = c(-0.1, -.5, -0.01, -0.5), col = "grey80", lwd = 1) #Plotting the Japan geometry. The expandBB argument allows us to control the size of the bounding box. The col argument colours Japan. The lwd argument controls the line width outlining the country.
plot(st_geometry(Occurence_Data_sf), add = TRUE, cex = .4, col = "red") #Adding the occurrence records.
plot(st_geometry(World_map_detail), add = TRUE) #Adding a map of the whole world. This helps orientate the audience by showing Korea and the edge of China.
```

### Part 5 (1 Available Point)
Download climate data. The below chunk downloads a raster that contains the average monthly temperature for a specific country. 

*Insert the name of the country identified in the previous chunks between the quotation marks.*

*KEY:* The country we want is Japan.

**Grading:** 1 point for successfully applying Japan to the country argument.

```{r}
Climate_Raster <- worldclim_country(country = "Japan", var = "tavg", res = 10, path=tempdir())
```

### Part 6 (1 Available Point)
The climate data raster (Climate_Raster) contains 12 layers. Each layer of the raster is the average temperature for a given month. Subset the raster to isolate only the December layer.

*KEY:* The layers are in order from January to December. Therefore, you can isolate the layer for December by sub-setting out layer 12.

**Grading:** 1 point for successfully sub-setting the month of December.

```{r}
Climate_Raster11 = subset(Climate_Raster, 12)
```

### Part 7 (2 Available Point)
Plot the climate data raster onto the map created in Part 4. Make sure to include occurrence records. Note, when using the plot function, the order you add plot layers is very important.

**Grading:** 1 point for successfully plotting the climate data. 1 point for plotting the occurrence records on-top of the climate raster.

```{r}
plot(Climate_Raster11) #Adding the climate raster first. This makes it the base for our plot, everything else we add is added on top of this raster.
plot(st_geometry(japan), lwd = 1, add = TRUE)
plot(st_geometry(Occurence_Data_sf), add = TRUE, cex = .4, col = "blue") #Switching the colour of occurrence points to blue to make them more identifiable.
plot(st_geometry(World_map_detail), add = TRUE)
```