---
title: "GeoR_Assign1_Katchen"
author: "Jordan Katchen"
date: "2023-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Library

```{r}
library(rgbif)
library(sf)
library(tidyr)
library(spData)        # load map data
```

## Step 1
Find Country Codes
```{r}
enumeration_country()
```

Search GBIF for Japanese green woodpecker (Picus awokera) occurrence records. Limit the results to 1000.
```{r}
GBIF <- occ_search(
  taxonKey = NULL,
  scientificName = "Picus awokera",
  country = NULL,
  publishingCountry = NULL,
  hasCoordinate = NULL,
  typeStatus = NULL,
  recordNumber = NULL,
  lastInterpreted = NULL,
  continent = NULL,
  geometry = NULL,
  geom_big = "asis",
  geom_size = 40,
  geom_n = 10,
  recordedBy = NULL,
  recordedByID = NULL,
  identifiedByID = NULL,
  basisOfRecord = NULL,
  datasetKey = NULL,
  eventDate = NULL,
  catalogNumber = NULL,
  year = NULL,
  month = NULL,
  decimalLatitude = NULL,
  decimalLongitude = NULL,
  elevation = NULL,
  depth = NULL,
  institutionCode = NULL,
  collectionCode = NULL,
  hasGeospatialIssue = NULL,
  issue = NULL,
  search = NULL,
  mediaType = NULL,
  subgenusKey = NULL,
  repatriated = NULL,
  phylumKey = NULL,
  kingdomKey = NULL,
  classKey = NULL,
  orderKey = NULL,
  familyKey = NULL,
  genusKey = NULL,
  speciesKey = NULL,
  establishmentMeans = NULL,
  degreeOfEstablishment = NULL,
  protocol = NULL,
  license = NULL,
  organismId = NULL,
  publishingOrg = NULL,
  stateProvince = NULL,
  waterBody = NULL,
  locality = NULL,
  occurrenceStatus = "PRESENT",
  gadmGid = NULL,
  coordinateUncertaintyInMeters = NULL,
  verbatimScientificName = NULL,
  eventId = NULL,
  identifiedBy = NULL,
  networkKey = NULL,
  verbatimTaxonId = NULL,
  occurrenceId = NULL,
  organismQuantity = NULL,
  organismQuantityType = NULL,
  relativeOrganismQuantity = NULL,
  iucnRedListCategory = NULL,
  lifeStage = NULL,
  isInCluster = NULL,
  limit = 1000,
  start = 0,
  fields = "all",
  return = NULL,
  facet = NULL,
  facetMincount = NULL,
  facetMultiselect = NULL,
  skip_validate = TRUE,
  curlopts = list()
)
```

Isolate the occurrence data as a TBL (data) from the GBIF list created above.
```{r}
Occurence_Data <- GBIF$data
Occurence_Data <- Occurence_Data %>% drop_na(decimalLatitude) #Remove rows with no lat data
Occurence_Data <- Occurence_Data %>% drop_na(decimalLongitude) #Remove rows with no Long data
```

Convert the the Lat and Long data in Occurence_Data to a sf geometry column.
```{r}
Occurence_Data_sf <- st_as_sf(Occurence_Data, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```

Where are these woodpeckers found? Plotting the occurence records on a world map.
```{r}
world_data <- world
plot(st_geometry(world))
plot(st_geometry(Occurence_Data_sf), add = TRUE, cex = .01, col = "blue")
```

Focusing in on the country the these woodpeckers are endemic to.
```{r}
japan <- world[world$name_long == "Japan", ]
plot(st_geometry(japan), expandBB = c(1, 1, 1, 1), col = "grey70", lwd = 1)
plot(st_geometry(Occurence_Data_sf), add = TRUE, cex = .4, col = "red")
plot(st_geometry(world), add = TRUE)
```