---
title: "GeoR_Assingment1_Katchen"
author: "Jordan Katchen"
date: "2023-02-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## library
This chunk contains all the packages required to complete this assignment. You may load additional packages if you wish, however, it is not required.

```{r}
library(rgbif)     # Used to load GBIF data
library(sf)
library(tidyr)
library(rnaturalearth)        # Used to load map data
library(geodata)    # Used to load in raster data
library(terra)
```

## Data Load
The bellow chunks load the data required for this assignment.

Search GBIF for Japanese green woodpecker (Picus awokera) occurrence records. Limit the results to 2500. Returns an object of class gbif, which is a S3 class list, with slots for metadata (meta), the occurrence data itself (data), the taxonomic hierarchy data (hier), and media metadata (media).
```{r}
GBIF <- occ_search(
  scientificName = "Picus awokera",
  limit = 2500
)
```

Isolating the occurrence data from the gbif object.
```{r}
Occurence_Data <- GBIF$data
```

Loading in a detailed map of the world from the naturalearth database. The map is loaded in as an sf object.
```{r}
World_map_detail <- ne_download(
  scale = 10,
  type = "countries",
  category = c("cultural"),
  destdir = tempdir(),
  load = TRUE,
  returnclass = c("sf")
)
```

## Assingnment

### Part 1
The first step will be to remove all rows with NA values in the latitude and longitude columns from the Occurence_Data. Note, there are many different ways to accomplish this task!

```{r}

```

### Part 2
Convert the Occurence_Data to an sf object.

```{r}

```

### Part 3
Where in the world are Japanese green woodpeckers found? Plot the occurrence records on a world map.

```{r}

```

### Part 4
Now that you have narrowed down the region of the world these woodpeckers are found, create a smaller map, just large enough to include all the occurrence records. Try your best to make your map visually appealing and functional, so feel free to be creative.

```{r}

```

### Part 5

Download climate data. The below chunk downloads a raster that contains the average monthly temperature for a specific country. 

*Insert the name of the country identified in the previous chunks between the quotation marks.*
```{r}
Climate_Raster <- worldclim_country(country = "INSERT HERE", var = "tavg", res = 10, path=tempdir())
```

### Part 6
The climate data raster (Climate_Raster) contains 12 layers. Each layer of the raster is the average temperature each month. Subset the raster to isolate only the December layer.

```{r}

```

### Part 7
Plot the climate data raster onto the map created in Part 4. Note, when using the plot function, the order you add plot layers is important.

```{r}

```